---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# syncdr

<!-- badges: start -->

<!-- badges: end -->

{syncdr} is an R package designed to facilitate the process of directory
comparison and synchronization. This package provides essential tools
for users who need to manage and synchronize their directories
effectively.

With {syncdr}, users can:

-   Visualize Directory Structures: Gain a comprehensive view of
    directory contents, including the tree structure, common files, and
    files unique to each directory.

-   Manage Files with Ease: Perform content-based and modification
    date-based file comparisons, and handle tasks like identifying
    duplicates, copying, moving, and deleting files seamlessly within
    the R environment. By incorporating {syncdr} into their workflow,
    users can achieve a more organized and up-to-date file system,
    simplifying the overall management and synchronization of
    directories.

## Installation

You can install the development version of syncdr from
[GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("RossanaTat/syncdr")
```

## Usage example

```{r example}

library(syncdr)

# Generate toy directories to show package usage

# --- Create syncdr.env --- #
syncdr.env <- toy_dirs()
left       <- syncdr.env$left
right      <-  syncdr.env$right

# --- Compare synchronization status of the two directories --- #
# comparing by date of last modification
sync_status <- compare_directories(left_path   = left,
                                   right_path  = right)

# --- Display synchronization status --- #
#  TO BE COMPLETED


```

