---
title: "Asymmetric Synchronization Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Asymmetric Synchronization Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

```

```{r}
library(syncdr)
#devtools::load_all(".")

# Create .syncdrenv
.syncdrenv = toy_dirs()

# Get left and right directories' paths 
left  <- .syncdrenv$left
right <- .syncdrenv$right

```


This article covers functions designed for ***asymmetric synchronization*** between two directories.

## What is asymmetric synchronization?

This is a **one-way** synchronization: you have a *master/leader* directory, and you want changes made there to be reflected in a *secondary/follower* directory.

⏭️ For all synchronization functions below, note that synchronization occurs ***from left to right.*** This mean that the right directory will **mirror** the contents of the left directory.

**To keep in mind:**

You need to use the output of `compare_directories()` as input for these functions. In doing so,

-   Ensure that the "leader" directory is passed to the path_left argument and the "follower" directory to the path_right argument (more examples below)
-   Make sure to set `by_date` and `by_content` arguments in `compare_directories()` the same way you pass them to the asymmetric synchronization functions. By default, `by_date = TRUE` and `by_content = FALSE` in every sync function.

## Types of asymmetric synchronization

`syncdr` allows to perform a ***specific set of asymmetric synchronization actions***, so that you can choose which one to execute depending on your needs

+--------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------+
| ::: {style="color:#0070FF"}                                        | ::: {style="color:#0070FF"}                                                                                                                                            | ::: {style="color:#0070FF"}                                                                                                     |
| Type of synchronization                                            | Actions on common files                                                                                                                                                | Actions on non-common files                                                                                                     |
| :::                                                                | :::                                                                                                                                                                    | :::                                                                                                                             |
+====================================================================+========================================================================================================================================================================+=================================================================================================================================+
| Full asymmetric synchronization:                                   | -   If comparing by date only (`by_date = TRUE`): Copy files that are newer in the left directory to the right directory.                                              | -   Copy to the right directory those files that exist only in the left directory.                                              |
|                                                                    | -   If comparing by date and content (`by_date = TRUE` and `by_content = TRUE`): Copy files that are newer and different in the left directory to the right directory. |                                                                                                                                 |
| **`full_asym_sync_to_right()`**                                    | -   If comparing by content only (`by_content = TRUE`): Copy files that are different in the left directory to the right directory                                     | -   Delete from the right directory those files that are exclusive in the right directory (i.e., missing in the left directory) |
+--------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------+
| Partial asymmetric synchronization -common files:                  | -   if `by_date = TRUE` only: copy files that are newer in left to right                                                                                               | no actions                                                                                                                      |
|                                                                    |                                                                                                                                                                        |                                                                                                                                 |
| **`common_files_asym_sync_to_right()`**                            | -   if `by date = TRUE` and `by_content = TRUE`: copy files that are newer and different in left to right                                                              |                                                                                                                                 |
|                                                                    |                                                                                                                                                                        |                                                                                                                                 |
|                                                                    | -   if `by_content = TRUE` only: copy files that are different in left to right                                                                                        |                                                                                                                                 |
+--------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------+
| Full asymmetric synchronization of non common files                | no actions                                                                                                                                                             | -   copy those files that are only in left to right                                                                             |
|                                                                    |                                                                                                                                                                        |                                                                                                                                 |
| **`update_missing_files_asym_to_right()`**                         |                                                                                                                                                                        | -   delete in right those files that are only in right (i.e., files "only in right" or in other words missing in left)          |
+--------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------+
| Partial asymmetric asymmetric synchronization of non common files: | no actions                                                                                                                                                             | -   copy those files that are only in left to right                                                                             |
|                                                                    |                                                                                                                                                                        |                                                                                                                                 |
| **`partial_update_missing_files_asym_to_right()`**                 |                                                                                                                                                                        | -   keep in right those files that are only in right (i.e., files 'missing in left')                                            |
+--------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------+

: Types of asymmetric synchronization

Let's see them in actions through the examples below:

##### \*️⃣ **Note: `verbose = TRUE`**

When executing any synchronization, you have the option to enable verbose mode by setting `verbose = TRUE`. This will display the tree structure of *both* directories BEFORE and AFTER the synchronization

**1 - Full asymmetric synchronization:**

```{r}

# With leader/master directory being the left directory 
sync_status <- compare_directories(left_path  = left,
                                   right_path = right,
                                   by_content = TRUE,
                                   verbose    = TRUE)

full_asym_sync_to_right(sync_status = sync_status,
                        by_content  = TRUE,
                        verbose     = TRUE)

# With leader/master directory being the right directory 
sync_status <- compare_directories(left_path  = right,  #notice args changing here
                                   right_path = left,
                                   by_content = TRUE,
                                   verbose    = TRUE)

full_asym_sync_to_right(sync_status = sync_status,      
                        by_content  = TRUE,
                        verbose     = TRUE)
```

**2 - Partial asymmetric synchronization -common files:**

```{r include=FALSE}


.syncdrenv.2 <- syncdr:::copy_temp_environment()

# Get left and right directories' paths 
left  <- .syncdrenv.2$left
right <- .syncdrenv.2$right
```

```{r}

sync_status <- compare_directories(left_path  = left,
                                   right_path = right)

common_files_asym_sync_to_right(sync_status = sync_status,
                                verbose     = TRUE)
```

**3 - Full asymmetric synchronization -non common files:**

```{r include=FALSE}

.syncdrenv.3 <- copy_temp_environment()

# Get left and right directories' paths 
left  <- .syncdrenv.3$left
right <- .syncdrenv.3$right

```

```{r}

sync_status <- compare_directories(left_path  = left,
                                   right_path = right)

update_missing_files_asym_to_right(sync_status = sync_status,
                                   verbose     = TRUE)

```

**4 - Partial asymmetric synchronization -non common files:**

```{r include=FALSE}

.syncdrenv.4 <- copy_temp_environment()

# Get left and right directories' paths 
left  <- .syncdrenv.4$left
right <- .syncdrenv.4$right

```

```{r}

sync_status <- compare_directories(left_path  = left,
                                   right_path = right)

partial_update_missing_files_asym_to_right(sync_status = sync_status,
                                           verbose     = TRUE)

```
