---
title: "Auxiliary Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Auxiliary Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(syncdr)
#devtools::load_all(".")
```

`syncdr` provides some auxiliary functions that might come in handy to better understand the content of your directories, even before taking certain synchronization actions.

To see some examples, let's start with `toy_dirs()`, and generate two toy directories.

```{r setup}

# Create syncdr.env with left and right directories
syncdr.env =toy_dirs()

# Get left and right directories' paths 
left  <- syncdr.env$left
right <- syncdr.env$right

```

**Search for duplicate files**

One useful auxiliary function is **`search_duplicates()`**, designed to generate a list of duplicate files within your directory. Duplicate files are identified based on identical content, regardless of their filenames. By default, `verbose = TRUE` will show you the list of duplicate files. To return it invisibly, set `verbose = FALSE`. In this latter case, a message will still pop up to let you know when the identification of duplicates is completed.

```{r}

# example
search_duplicates(right, verbose = TRUE)
```

-   **COMMENT ON NEXT STEPS:** Before adding more auxiliary functions, I need to better understand which functions among those that I have created should be internal vs exported. Also, I need to improve the structure of those functions to make sure there is no redundant code (e.g., more functions than needed). Current auxiliary functions are used to:

    -   *style text messages*

    -   *filter files by directory, by date, by content, by date and content*

    -   *retrieve info about one directory*

    -   *compare modification times of files*

    -   *compare file contents*

    -   *hashing files*

*(For more details refer to the auxiliary_functions.R file and the functions documentation)\
*
