---
title: "Auxiliary Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Auxiliary Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(syncdr)
#devtools::load_all(".")
```

`syncdr` provides some auxiliary functions that might come in handy to better understand the content of your directories, even before taking certain synchronization actions.

To develop some examples, let's start by calling `toy_dirs()`. This auxiliary function creates toy directories within the syncdr environment, containing samples common files as well as files exclusive to either directory. These toy directories are deleted every time a new session is started. 
```{r setup}

# Create .syncdrenv with left and right directories
.syncdrenv =toy_dirs()

# Get left and right directories' paths 
left  <- .syncdrenv$left
right <- .syncdrenv$right

```

Together with `toy_dirs()`, you might want to use `copy_temp_environment()`, in order to copy the original environment and play with the various {syncdr} functions on this copied environment rather than the original one which remains untouched. 

**Search for duplicate files**

One useful auxiliary function is **`search_duplicates()`**, designed to generate a list of duplicate files within your directory. Duplicate files are identified based on identical content, regardless of their filenames. By default, `verbose = TRUE` will show you the list of duplicate files. To return it invisibly, set `verbose = FALSE`. In this latter case, a message will still pop up to let you know when the identification of duplicates is completed.

```{r}

# example
search_duplicates(right, verbose = TRUE)
```

