---
title: "Auxiliary Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Auxiliary Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

devtools::load_all(".")
```

```{r setup}
#library(syncdr)
```

`syncdr` provides some auxiliary functions that might come in handy to better understand the content of your directories, even before taking certain synchronization actions.

To see some examples, let's start with `toy_dirs()`, and generate two toy directories.

```{r}

# Create syncdr env with left and right directories
syncdr.env <- toy_dirs()

# Get left and right directories' paths 
left  <- syncdr.env$left
right <- syncdr.env$right

```

**Search for duplicate files**

One useful auxiliary function is **`search_duplicates()`**, designed to generate a list of duplicate files within your directory. Duplicate files are identified based on identical content, regardless of their filenames.

```{r}

# example
search_duplicates(right)
```

*COMMENT: Before adding more aux functions, I need to better understand which functions among those that I have written should be internal vs exported (e.f., hashing files, getting directory info, see auxiliary_function.R)*
