---
title: "Introduction to {syncdr}"
subtitle: "File Handling, Directory Comparison & Synchronization in R"
author: "Rossana Tatulli"
date: "2024-mm-dy"
output: 
rmarkdown::html_vignette:
  toc: true
vignette: >
  %\VignetteIndexEntry{Introduction to {syncdr}}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#library(syncdr)
```

## Why {syncdr}? 

**{syncdr}** is an R package for handling and synchronizing files and directories. Its primary objectives are:

1.  To provide a clear snapshot of the content and status of synchronization between two directories under comparison: including their tree structure, their common files, and files that are exclusive to either directory
2.  To help make file handling in R easier: Enabling content-based and modification date-based file comparisons, as well as facilitating tasks such as duplicate identification, file copying, moving, and deletion *(todo: better describe this point later on depending on functionalities)* .

------------------------------------------------------------------------

💡\
This article does not offer a comprehensive overview of **{syncdr}** functionalities. After familiarizing yourself with this general workflow, read the articles throughout the rest of this website..they will introduce all main features of **{syncdr}** in a structured way.

---

## Synchronizing with {syncdr}
**Learn how to work with {syncdr} and compare and synchronize directories in R**

### Step 1: ...
