---
title: "Introduction to {syncdr}"
subtitle: "File Handling, Directory Comparison & Synchronization in R"
author: "Rossana Tatulli"
date: "2024-mm-dy"
output: 
rmarkdown::html_vignette:
  toc: true
vignette: >
  %\VignetteIndexEntry{Introduction to {syncdr}}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
devtools::load_all(".")
```

## Why {syncdr}?

**{syncdr}** is an R package for handling and synchronizing files and directories. Its primary objectives are:

1.  To provide a clear snapshot of the content and status of synchronization between two directories under comparison: including their tree structure, their common files, and files that are exclusive to either directory
2.  To make file handling in R easier: i.e., enabling content-based and modification date-based file comparisons, as well as facilitating tasks such as duplicates identification, file copying, moving, and deletion.

------------------------------------------------------------------------

💡\
This article does ***not*** offer a comprehensive overview of **{syncdr}** functionalities. Rather it provides a sample workflow for working with the package's main functions . After familiarizing yourself with this general workflow, read the articles throughout the rest of this website -they will explore all features of **{syncdr}** in a structured way.

------------------------------------------------------------------------

## Synchronizing with {syncdr}

**Learn how to work with {syncdr} and compare and synchronize directories in R**

Suppose you are working with two directories, let's call them `left` and `right` -each containing certain files and folders/sub-folders.

To get started, let's call `syncdr` function `toy_dirs()`, which generates two toy directories in `syncdr.env` environment -say `left` and `right`- that we can use to showcase `syncdr` functionalities.

```{r toy-dirs}

# Create syncdr env with left and right directories
syncdr.env <- toy_dirs()

# Get left and right directories' paths 
left  <- syncdr.env$left
right <- syncdr.env$right

```

You can also quickly compare the two directories tree structure by calling `display_dir_tree()`. By default, it fully recurses -i.e., shows the directory tree of all sub-directories. However, you can also specify the number of levels to recurse using the `recurse` argument.

```{r display-toy-dirs}

# Visualize left and right directories' tree structure 
display_dir_tree(path_left  = left,
                 path_right = right)

```

### Step 1: Compare Directories

The most important function in `syncdr` is `compare_directories()`. It takes the paths of left and right directories and determines their synchronization status *(see below)*. This function represents the backbone of `syncdr`: you should always start by calling this function, retrieve the `syncdr_status` object it generates, and utilize this object both:

-   to *inspect* the synchronization status of files present in both directories as well as those exclusive to either directory

-   as the input for all other functions within `syncdr` that facilitate *synchronization* actions on the directories under comparison*.*

Note that `compare_directories()` allows you to compare the two directories in 3 ways:

1.  By **date** only -*the default:*

| sync_status (*all* *common files)* |
|:----------------------------------:|
| older in left, newer in right dir  |
|  newer in left, olderin right dir  |
|             same date              |

2.  By **date and content**, by specifying `by_content = TRUE` (by default `by_date = TRUE` if not specifically set to FALSE)

| sync_status (*common files that are newer in either directories, i.e., not of same date )* |
|:--------------------------------------------------------------------------------------------:|
|                                     different content                                      |
|                                        same content                                        |

3.  By **content** only, by specifying `by_date = FALSE` and `by_content = TRUE`

| sync_status (*all* *common files)* |
|:----------------------------------:|
|         different content          |
|            same content            |

In each of these cases, the sync_status for files that are exclusive to either directory is

| sync_status (*non* *common files)* |
|:----------------------------------:|
|            only in left            |
|           only in right            |

```{r step-1}

# Compare by date only -the Default
compare_directories(left, 
                    right)

# Compare by date and content 
compare_directories(left, 
                    right,
                    by_content = TRUE)


# Compare by content only 
compare_directories(left, 
                    right,
                    by_date    = FALSE,
                    by_content = TRUE)

```

#### Exploring compare_directories() output 

### Step 2: Visualize Synchronization Status 

### Step 3: Synchronize directories 
